Supporting Information

### 2018-03-30 SupportingInformation.Rmd
there was a problem with checkpoint, it would reinstall with every knit. I think I have fixed it

<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
library(checkpoint)
checkloc<-"./.checkpoint"
if (!dir.exists(checkloc))
{
  dir.create(checkloc)
  checkpoint("2018-03-29",checkpointLocation = checkloc)
}
```

>>>>

<!--checkpoint package-->
```{r checkpoint_chunk, echo=F, warning=F, message=F, results="hide"}
library(checkpoint)
#checkloc<-tempdir()
#if (!dir.exists(paste0(checkloc,"/.checkpoint/")))
#{
#  dir.create(paste0(checkloc,"/.checkpoint/"))
#  checkpoint("2018-03-29",checkpointLocation = checkloc)
#}
if (!dir.exists("./.checkpoint/"))
{
  dir.create("./.checkpoint/")
}
checkpoint("2018-03-29",checkpointLocation = "./")
```
